---
output:
  revealjs::revealjs_presentation:
    theme: moon
    transition: none
    slide_level: 1
    reveal_options:
      slideNumber: true
      fig_caption: false
      navigation: linear
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(ggplot2)
```

# https://cscar.research.umich.edu

- Free Consultations
    - with a GSRA
        - Self-scheduled or first come first serve, same-day or next day
    - with a PhD Statistician
        - Email deskpeople@umich.edu, wait can be anywhere from a few days to a few weeks
- Email help list
    - stats-consulting@umich.edu
- Workshops
    - https://teachtech.umich.edu
- Paid work

# When to talk to a statistician?

- As early as possible!
    - Study design
    - Power analysis
    - Does your data allow you to answer your research questions?
- Carrying out analysis
    - Suggestions on analysis techniques
    - Choosing an appropriate software
    - Detecting issues
    - Debugging
- Interpreting results

# Understanding your data

```{r, echo = FALSE, message = FALSE, fig.height = 2.5, fig.width = 3, fig.show="hold"}
ggplot(diamonds, aes(x = log(price))) + geom_histogram() +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())
ggplot(diamonds, aes(x = price)) + geom_histogram() +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())
```

```{r, echo = FALSE, message = FALSE, fig.height = 2.5, fig.width = 3, fig.show="hold"}
ggplot(diamonds, aes(x = carat, y = price)) + geom_point() +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())

data<-data.frame(Study_ID = c("100", "100", "100", "200", "200", "200", "300",
                              "300", "300"),
                 time_point = c("Time1", "Time2", "Time3", "Time1", "Time2",
                                "Time3", "Time1", "Time2", "Time3"),
                 value = c(15, 50, 120, 20, 35, 150, 35, 67, 95))

ggplot(data, aes(x = time_point, y = value, group = Study_ID, color = Study_ID)) +
  geom_point() + geom_line() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")

```

# Analysis

- 2 group comparison: t-test
- Anything beyond that: Regression modeling
    - Linear regression
    - Generalized linear regression
    - Mixed effects regression
    - Generalized mixed effects regression
- ANOVA = linear regression
- GIS help: https://gis.umich.edu
